\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
reads better

The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical, physical volume objects, GDML parameters and material classes.
The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} 
class in Python. The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments 
in \PYGEOMETRY{} are described.

>>>>

The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical volumes, physical volumes, GDML parameters and material classes.
The constructors of the Python classes are kept as close to the original Geant4 C++ implementation so that \PYGEOMETRY{} users do not have to learn 
a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{pyg4ometry.geant4.solid.Box} 
class in Python. The Python object constructor is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments 
in \PYGEOMETRY{} are described.
